---
title: 'Twitter Friends Ego Graph Scraper `r icon::fa("twitter", color = "white", size = 1)`'
author: '**Pietro Monticone** [`r icon::fa("github", color = "white")`](https://github.com/pitmonticone) | **Claudio Moroni** [`r icon::fa("github", color = "white")`](https://github.com/claudio20497) | **Davide Orsenigo** [`r icon::fa("github", color = "white")`](https://github.com/dadorse)'
date: '*University of Turin* | `r format(Sys.time(), "%d %B %Y")`'
output:
 prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	eval = FALSE,
	include = TRUE,
	message = FALSE,
	warning = FALSE,
	paged.print = FALSE
)
```

## **Packages** 

```{r packages}
# Data Science
library(tidyverse)
# Twitter Scraping
library(rtweet)
```

## **Functions**

```{r functions}
# Download the list of all the followes of EGO
friend_egonetwork_first <- function(ego){
  ego_friends <- get_friends(
    ego,
    retryonratelimit = TRUE)
### Rename variables
names(ego_friends) <- c("Source","Target")
### Store dataset in .csv file 
###write.csv(as.data.frame(ego_friends), "friends.csv")
return(ego_friends)
}

# Download the tibble of all the followes of the followeea of EGO
follower_egonetwork_first <- function(ego){
  ego_followers <- get_followers(
    ego,
    n = 75000,
    retryonratelimit = TRUE)
  
  #ego_followers_ids <- ego_followers$user_id
  #names(ego_followers) <- c("Source","Target")
  #write.csv(as.data.frame(ego_friends), "data/friends.csv")
  return(ego_followers)
}

# Download the tibble of all the followes of the followeea of EGO
friend_egonetwork_second <- function(ego){
egonetwork_first(ego)

ego_friends_friends <- tibble()
friend <- 1
flag <- TRUE
  
while( friend <= length(ego_friends_ids ) ) {
  print(friend)
  if( flag ){ 
    new_friend <- get_friends(
        ego_friends_ids[friend],
        retryonratelimit = TRUE)
    
    ego_friends_friends <- bind_rows(ego_friends_friends, new_friend) 
      
    if( friend %% 15 == 0 ){ flag <- FALSE } 
        friend <- friend + 1
    }
    else {
      print( now() )
      Sys.sleep(15.1 * 60)
      flag <- TRUE 
    } 
}
### Rename variables 
names(ego_friends_friends) <- c("Source","Target")
### Store dataset in .csv file 
###write.csv(as.data.frame(ego_friends_friends), "friends_friends.csv")
return(ego_friends_friends)
}
```

## **Store Twitter API Keys**

```{r credentials}
api_key <- "XXXXX"
api_secret_key <- "YYYYY"
access_token <- "ZZZZ"
access_token_secret <- "KKKKK"
```

## **Authenticate via Web Browser** 

```{r authentication}
token <- create_token(
  app = "app_name",
  consumer_key = api_key,
  consumer_secret = api_secret_key,
  access_token = access_token,
  access_secret = access_token_secret)
```

## **Get Friends**

Download all the Twitter friends (i.e. first order followees) of [\@ClaudioMoroni3](https://twitter.com/ClaudioMoroni3).

```{r get-claudio-friends}
# Get the tibble of friends of @ClaudioMoroni3
claudio_friends <- friend_egonetwork_first("ClaudioMoroni3")

# Store dataset in .csv file 
write.csv(as.data.frame(claudio_friends), "claudio_friends.csv")
```

Download all the Twitter friends (i.e. first order followees) of [\@PietroMonticone](https://twitter.com/PietroMonticone).

```{r get-pietro-friends}
# Get the tibble of friends of @PietroMonticone
pietro_friends <- friend_egonetwork_first("PietroMonticone")

# Store dataset in .csv file 
write.csv(as.data.frame(pietro_friends), "pietro_friends.csv")
```

## **Get Friends of Friends**

Download all the Twitter friends of friends (i.e. second order followees) of [\@ClaudioMoroni3](https://twitter.com/ClaudioMoroni3).

```{r get-claudio-friends-friends}
# Get the tibble of friends of friends of @ClaudioMoroni3
claudio_friends_friends <- friend_egonetwork_second("ClaudioMoroni3")

# Store dataset in .csv file 
write.csv(as.data.frame(claudio_friends_friends), "claudio_friends_friends.csv")
```

Download all the Twitter friends of friends (i.e. second order followees) of [\@PietroMonticone](https://twitter.com/PietroMonticone).

```{r get-pietro-friends-friends}
# Get the tibble of friends of friends of @PietroMonticone
pietro_friends_friends <- friend_egonetwork_second("PietroMonticone")

# Store dataset in .csv file 
write.csv(as.data.frame(pietro_friends_friends), "pietro_friends_friends.csv")
```
